---
title: "Part 2"
author: "Yineng Chen"
date: "6/24/2020"
output: 
  html_document:
    keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load data and exploratory data analyses

```{r}
data("ToothGrowth")

table(ToothGrowth$supp)
table(ToothGrowth$dose)

boxplot(len ~ dose, data = ToothGrowth, col = "lightgray")
boxplot(len ~ supp, data = ToothGrowth, col = "lightgray")
```


###  Summary

```{r}
summary(ToothGrowth)
```

### compare tooth growth by supp and dose

##### By supp

```{r}
supp1 = subset(ToothGrowth, ToothGrowth$supp =="OJ")
supp2 = subset(ToothGrowth, ToothGrowth$supp =="VC")

t = t.test(supp1$len,supp2$len)

mean1 = mean(supp1$len)
sd1 = sd(supp1$len)

mean2 = mean(supp2$len)
sd2 = sd(supp2$len)

p = t$p.value
ci = t$conf.int
ts = t$statistic

out3 = cbind(mean1,mean2,p,ci[1],ci[2])
colnames(out3) = c("OJ","VC","p value","lower limit","upper limit")
out3
```

**conclusion:**

With a significant level of 5%, the mean len in group OJ is not significantly different from group VC ( t = `r ts`, p value = `r p`)

##### By dose

```{r}
alpha = 0.05
alpha_adj = alpha/choose(3,2)
```

```{r}
pt = pairwise.t.test(ToothGrowth$len, ToothGrowth$dose, p.adj='bonferroni')

pt$p.value
```

**conclusion:**

Adjusting p values with bonferroni medhod, the results shows that there are difference in the mean of len between Dose 0.5 vs. Dose 1, Dose 0.5 vs. Dose 2, and Dose 1 vs. Dose 2.